Congestion-Aware Join Optimization in Key-Value Stores

### 2014-08-04 paper/paper.tex
Add missing diagrams for paper
Add more to architecture section

\begin{figure}
    \centering
    \missingfigure{Topology graph}
    \caption{Sample network topology}\label{fig:sample-topology}
\end{figure}

@@

\begin{figure}
    \centering
    \missingfigure{ER diagram}
    \caption{Simple query entities}\label{fig:entities}
\end{figure}

@@

Our system uses OpenFlow~\cite{McKeown2008} enabled switches to allow centralized network control.
We currently pass all queries through our SDN controller which is running on the POX~\cite{Gude2008} platform.

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/sample-topology.pdf}
    \caption{Sample network topology}\label{fig:sample-topology}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/rubis-er.pdf}
    \caption{Simple query entities}\label{fig:entities}
\end{figure}

@@

Our system uses OpenFlow~\cite{McKeown2008} enabled switches to allow centralized network control.
We currently pass all queries through our SDN controller which is running on the POX~\cite{Gude2008} platform.
Each host on the network contains a simple document store which is capable of answering requests both from client queries and other servers in the network.
When a query is received from a client, the server looks up entities on the left-hand side of the join in its local storage and requests the entities on the right side of the join from other servers in the network.
When a server receives a request from another server, it looks up the necessary entities to be joined locally and sends the reply back to the requesting server.
Once the server processing a client request receives responses from the other servers on the network, it can send a final response back to the client.

This results in the issue of stragglers we presented previously.
Note that the common technique of issuing a request multiple times to avoid stragglers is not helpful in our scenario.
As previously stated, our performance is bottlenecked by the available bandwidth.
Stragglers exist in our system because of a lack of available bandwidth as opposed to variations in node performance (which is what multiple issuance is designed to mitigate).
Furthermore, multiple issuance would place even stronger bandwidth pressure on our network, causing additional performance issues.
Instead, we mitigate the effect of stragglers by adjusting the bandwidth allocation for each flow.
